TSELM: Target speaker extraction using discrete tokens and language models

### 2024-09-09 src/paper.tex
update

\begin{table*}
    \caption{The performance of different systems on Libri2Mix testset. "G" means generative while "D" means discriminative. For discrete models,
    we compute the speaker similarity with the discretized target speech 
    (Target-discrete-WavLM). We use "\_d" to denote it.  }
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.2}
    \begin{center}
        \begin{tabular}{ccccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Category} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{5-7}
              &                   &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            Mixture                 & - & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-Discrete   & G & -                          & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   &  D & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            \hline
            Continuous-WavLM-L6   & G    & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid    & G       & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            TSELM-S-NoConcat           & G       & Discrete                    & 354M                        & 3.47    & 4.03    & 3.19   & 69.6\%                & 0.868\_d                 \\
            \hline
            TSELM-S           & G       & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M          & G        & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L         & G         & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \label{main_exp}
      \end{center}
    %   \vspace{-10pt}
  \end{table*}

@@

  Spex+                   & D                                             & C                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
  Contin-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\

@@

  TSELM-S-NoConcat        & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline

>>>>

@@

  Spex+                   & D                                             & -                                                                                  & 3.36        & 3.76       & 2.98       & 19.3            & 0.923     &          & 3.36        & 3.76       & 2.98       & 19.3            & 0.923             \\ \hline
  Continuous-WavLM-L6     & G                                             & C                                                                                  & 3.56        & 4.06       & 3.27       & 14.7            & 0.877     &          & 3.56        & 4.06       & 3.27       & 14.7            & 0.877             \\

@@

  TSELM-S-NoCat       & G                                             & D                                                                                   & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d    &        & 3.47        & 4.03       & 3.19       & 69.6            & 0.868\_d         \\ \hline
